---
title             : "Reanalysis of Psychological Paper: Computer Game Play Reduces Intrusive Memories of Experimental Trauma via Reconsolidation-Update Mechanisms"
shorttitle        : "Reanalysis"

author: 
  - name          : "Ana-Louise Franz"
    affiliation   : ""
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "afranz100@gmail.com"

affiliation:
  - id            : "1"
    institution   : "Brooklyn College"




abstract: |
  There are a few moments in the creation and recollection of memory where this process can be interrupted. This can be used to help people who are suffering from the results of tramatic memories. This study examined the process of reconsolidation, the recollection of a memory, to determine if there is a way to inturrupt this process using a cognitive task. The cognitive task used in this experiment was a simple game of Tetris. 

  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "reconsolidation, cognitive task"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```



# Methods

## Participants
52 participants (31 female, 21 males) which consisted of university students and the general public. 65% of the participants were students. 

## Material
The details of the trauma exposure and the  reconsolidation task are detailed in James et al. (2015)

## Procedure
The experiment was performed both in the lab and at home in the form of a diary. They watched a traumatic film and were then assinged to either the cognitive task group or the no task (control) group.

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
